Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-01-30 revisionMemo/rev1.tex
more efforts from CD and MG

		TO DO: The reviewer is correct in that our paper addresses the majority of IR scholarship that misuses GLM approaches for dyadic data. We have rewritten these sentences in the following way: In practice, such strategies remain problematic because they do not directly address the fundamental data generating process but instead seek to correct for dependence while using a baseline model that makes strong assumptions about the independence of observations in the DGP. While corrections such as X and Y are beneficial at times for A and B, these approaches remain only partially useful, and do not sufficiently capture third-order dependencies that organically arise from dyadic data. 

@@

		TO DO: We have revised this opening statement to clarify our position. 

@@

>>>>

		TO DO in paper: Strategies like those employed by Aronow et al do not directly model all relevant dependencies in the data \footnote{As Aronow et al explain, “Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data." p. 16.} but instead adjust the variance estimator.  While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will cause us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

		 The point is well taken, we have clarified this section (on page 2) to point to the assumption of independence as the primary problem, not the stacking of observations in and of itself.

@@

		\item \textcolor{blue}{ \emph{ MG/CD: We think the reviewer makes a good suggestion here to clarify, mathematically or in some other illustrative way, exactly how we think that dependencies bias the estimator. For example we can say that our target of inference is the estimation of beta (with some variance). If a coefficient is correlated with a dependency, then we could obtain an estimate for beta that is artificially high (and the same is true for the reverse).}}
	\item  \textcolor{blue}{ \emph{ What we think: True DGP: $Y = B0 + XB1 + a + b +$ 3rd order stuff + e
	\item What most do: $Y = \hat{B0} + X\hat{B1} + e$
	\item Something like if we have dependencies then $E(\hat{B1}) = E(B1) + cov(B1,$ other stuff)}}
